### 2013-12-16 research/paper/results/results-2.3.tex
Committing a single sentence explaining our new parameter is the same as Parkinson's
Committing what I think is my last bit before submission. Kasun still needs to fix some stuff up, there are notes in the document to him

The range of incident flow angles where $C_y$ remains positive is narrow at $\reynoldsnumber=165$ ($0^\circ <\theta \leq$ $6^\circ$) compared to $\reynoldsnumber=22300$ ($0^\circ <\theta \leq 15^\circ$). This feature is what sustains galloping. Power is only transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating body, as demonstrated by equation \ref{power_alt}. Incident angles beyond this range actually suppress the galloping and power goes in the opposite direction, i.e; form body to fluid. Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for $\reynoldsnumber=165$ compared to $\reynoldsnumber=22300$, it is expected that power output at $\reynoldsnumber=165$ is significantly lower than at $\reynoldsnumber=22300$.

@@

The efficiency of the system can be defined as the ratio of the time average power output to $P_{mean}=\rho U^3\frac{D}{2}$, the kinetic energy in the fluid approaching the body. A similar definition was given in \citet{Barrero-Gil2010a}). The current results show that the system has a peak efficiency of $0.26\%$  for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$. The peak efficiency reported in \citet{Barrero-Gil2010a} for $\reynoldsnumber=22300$ is approximately $5\%$ less than the current result. This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing at values of $\theta$ where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.

@@

\JL{KASUN: I don't understand the above paragraph. What is the main point of this paragraph? Are you trying to show that the only the terms dependent on $\dot{y}$ are dissipative, and so only those terms contribute to the transfer of energy or power to the body? That is true, but that is also true for VIV, so I don't see how that shows that the ``system is governed by the transverse velocity rather than the natural frequency''. I definitely don't understand that last sentence. Do you mean ``power'' when you say ``system''? The problem is that, as I've pointed out, the exact same argument regarding dissipation applies to VIV, which is strongly dependent on the natural frequency.}

@@

The natural time scales of the system can be found by solving for the eigenvalues of the linearized equation of motion, namely
\begin{equation}
\label{eqn:eom_linear}
(m{+}m_a)\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
\end{equation}
which is simply the equation of motion presented in equation \ref{final_equation_motion} with the polynomial series for the lift force truncated at the linear term, and the forcing term representing vortex shedding removed.

@@

In this form, $\lambda$ represents the inverse time scale of the of the motion of the body due to the negative damping effect of the long-time aerodynamic forces. In fact, the terms can be regrouped and $\lambda$ written as
\begin{equation}
  \label{eqn:timescale}
  \lambda = \frac{a_1}{m^*}\frac{U}{D}
\end{equation}

Written this way, the important parameters that dictate this inverse time scale are clear. The rate of change in the aerodynamic force with respect to angle of attackwhen the body is at the equilibrium position, $\partial C_y/\partial \alpha$, is represented by $a_1$. The mass ratio is represented by $m^*$. The inverse advective time scale of the incoming flow is represented by the ratio $U/D$. Increasing $a_1$ would mean the force on the body would increase more rapidly with small changes in the angle of attack, $\theta$, or transverse velocity. Equation \ref{eqn:timescale} shows that such a change will increase the inverse time scale, or analogously dcrease the response time of the body. Increasing the mass of the body, thereby increasing $m^*$, has the opposite effect. The inverse time scale is decreased, or as might be expected, a heavier body will take longer to respond.

This timescale can then be used to non-dimensionalize the equation of motion, and to find the relevant dimensionless groups of the problem. If the non-dimensional time, $\tau$, is defined such that $\tau=t(a_1/m^*)(U/D)$, the equation of motion presented in equation \ref{final_equation_motion} can be non-dimensionalized as
\begin{equation}
  \label{eqn:eom_nondim}
  \ddot{Y} + \frac{m^{*2}}{a_1^2}\frac{kD^2}{mU^2}Y = \left(\frac{1}{2} - \frac{m^*}{a_1}\frac{cD}{mU}\right)\dot{Y} \dots,
\end{equation}

where the coefficients can be regrouped into combinations of non-dimensional groups, and rewritten as
\begin{equation}
  \label{eqn:eom_nondim_regroup}
  \ddot{Y} + \frac{k^{*2}m^{*2}}{a_1^2}Y = \left(\frac{1}{2} - \frac{c^*m^*}{a_1}\right)\dot{Y} \dots,
\end{equation}

where $k^*=kD^2/mU^2$ is a non-dimensional stiffness parameter, and $c^*=cD/mU$ is a non-dimensional damping parameter.

Equation \ref{eqn:eom_nondim_regroup} shows there are four non-dimensional parameters that play a role in setting the response of the system. These are the stiffness $k^*$, the damping $c^*$, the mass ratio $m^*$, and the rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $a_1$. The grouping of these parameters into two groups in equation \ref{eqn:eom_nondim_regroup} which arise by non-dimensionalising using the natural time scale of the galloping system, suggests there are two groups that dictate the response: $\Gamma_1 = k^{*2}m^{*2}/a_1^2$ and $\Gamma_2 = c^*m^*/a_1$. For a given geometry and Reynolds number, $Gamma_1$ can be thought of as a combined mass-stiffness, whereas $\Gamma_2$ can be thought of a a combined mass-damping parameter. As it is assumed that during galloping the stiffnes plays only a minor role, $\Gamma_2$ seems a likely parameter to collapse the data presented in figure \ref{fig:uncollapsed_data}.

Figure \ref{fig:collapsed_data} presents the same data as shown in figure \ref{fig:uncollapsed_data}, but in terms of the parameter $\Gamma_2$. The collapse, especially of the velocity amplitude and power output data, is excellent. This result shows that it is possible to obtain a similar power output at different values of \ustar\ or $\zeta$ when the mass-damping constant, $\Gamma_2$, is kept fixed. An example of this is shown in Fig.\ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\Gamma_2=$\JL{KASUN: put the value of the mass-damping (your parameter $c/\rho\mathcal{A}U$) that you used here and in the figure caption}, are plotted. The figure clearly shows that the common power output is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.

@@

Power can be expressed as the product of force and velocity. Therefore the transferred power fromm the fluid to the body can be expressed as $P_t=F_y\dot{y}$, as shown in equation \ref{power_alt}. Similarly the dissipated power due to the mechanical damping could be expressed as $P_d=(c\dot{y})\dot{y}$ as shown in equation \ref{power}. The time average of these two quantities should be equal due to energy conservation, provided that the mechanical friction losses are neglected. The mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased. The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar. Time histories of $P_t $ and $P_d$ at each of these key regions are presented in figure \ref{fig:power_time_histories}.

\JL{KASUN: why have you established that it is the damping, not $U^*$, that is important, but here you persist with presenting results in terms of $U^*$? How do these regions correspond to regions on the curve in terms of your damping parameter (that I have labelled $\Gamma_2$)? Can you define these three regions in terms of this new parameter?}

It has been established earlier that the damping factor is a function of $U^*$. Therefore it could be derived that $U^*$ is inversely proportional to damping coefficient. Hence the damping coefficient reduces when you move from region 1 to 3. Fig \ref{fig:lift_curves} (a) shows that $C_y$ and therefore instantaneous force rises until $4^\circ$ where it peaks and then falls and at around $6^\circ$ becomes negative. The maximum amount of power that could be transferred occurs near the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$. Data at $\zeta=0.1$, $m^*=40$ and \reynoldsnumber=165 (Fig.\ref{fig:power_time_histories}) are analysed as and example.

\JL{KASUN: I don't understand the point of the above paragraph. What are you trying to say? That maximum power output occurs when the tranverse velocity is such that the lift force is a maximum?}

@@

@@

The mean power at different $m^*$ is presented as a function of the mass-damping parameter $\Gamma_2$ in figure \ref{fig:m_star_collapsed}(a) for the low \reynoldsnumber\ case. For $m^*>30$, the power output is essentially independent of $m^*$, while at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range. However, when the sinusoidal forcing function in equation \ref{equationofmotion}, which caters for the vortex shedding, is disregarded, the reduction in power is not observed as shown in figure \ref{fig:m_star_collapsed}(b). The suppression of galloping response at low $m^*$ and low \reynoldsnumber\ due to the presence of vortex shedding has previously been observed by \cite{Joly2012}. This is a non-linear interaction between the forcing that drives the galloping excitation and the forcing as a result of vortex shedding. The forcing associated with vortex  shedding is significantly larger and at a higher frequency than the forcing that drives galloping. Systems with low $m^*$ do not have enough inertia to fully sustain the galloping excitation over the longer period.

At $\reynoldsnumber=22300$ power output started to increase for cases with $m^*<50$. The overall mean power tend to increase as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios presented in Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same phenomenon occurring in both cases whereby the velocity signal tend to shift from a sinusoidal signal towards a square wave. The corresponding displacement signal tend to become more like a triangular wave. When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity. Higher velocities are favourable because they result in higher instantaneous hydrodynamic forcing and power output from mechanical damping. However, the velocity is limited by the characteristic of the hydrodynamics forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which correspond to a transverse velocity of $\frac{\dot{y}}{U}=0.235$.It is estimated that the efficiency limit i.e ($\ustar \rightarrow \infty$, $m^* \rightarrow 0$ and $\frac{c}{\rho U \mathcal{A}}=1.22$) will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing. Physical systems may not realize the full potential due to practical limitations. Increasing $U^*$ effectively reduces the stiffness of the system and lengthen the period, thus again allowing a larger portion of the period to be at a high velocity which favours power output. For the case of fixing $U^*$ and decreasing $m^*$ in (Fig\ref{fig:mstarcollapsed_parkinson} (a)), the lengthening of the period is associated with the added mass which is kept constant at 3.5 being more dominant on the overall mass of the system when m* is reduced.

\JL{KASUN, again this last paragraph is all in terms of $U^*$, but you establish earlier that $U*^$ is not the important parameter, your new damping parameter (which is actually a mass-damping parameter) is the critical parameter. Can this argument be rewritten in terms of this new parameter?}

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. At higher $m^*$ ($m^*>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised damping constant $\frac{c}{\rho U \mathcal{A}}$ . By analysing key regions of the power vs \ustar curve is concluded that in order to obtain an optimum power output, the mass-damping constant $\Gamma_2$ should be high, but not so excessive that it hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was also observed. The peak efficiency was found to be $0.26\%$ for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$  when $\Gamma_2=0.314$ and $\Gamma_2=1.04$ respectively. In the low \reynoldsnumber\ case, the mean power tends to decrease at $m^*<30$ which appears to be due to the influence of vortex shedding. At $\reynoldsnumber=22300$ the opposite is observed where the mean power tends to increase with decreasing mass ratio, as well as the mean power increasing with increasing $U^*$ at low mass ratios. For this higher \reynoldsnumber\ case, When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output. The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\frac{c}{\rho \mathcal{A}U}=1.22$ by analysing the data trend by lowering the $m^*$.

>>>>

The range of incident flow angles where $C_y$ remains positive is narrow at $\reynoldsnumber=165$ ($0^\circ <\theta \leq$ $6^\circ$) compared to $\reynoldsnumber=22300$ ($0^\circ <\theta \leq 15^\circ$). This feature is what sustains galloping. Power is only transferred from the fluid to the supporting structure within this range of incident angles because fluid forces are acting in the direction of travel of the oscillating body, as demonstrated by equation \ref{power_alt}. Incident angles beyond this range actually suppress the galloping and power goes in the opposite direction, i.e; from body to fluid. Therefore due to the overall smaller $C_y$ and narrow range of angles where $C_y$ is positive for $\reynoldsnumber=165$ compared to $\reynoldsnumber=22300$, it is expected that power output at $\reynoldsnumber=165$ is significantly lower than at $\reynoldsnumber=22300$.

@@

The efficiency of the system can be defined as the ratio of the time average power output to $P_{mean}=\rho U^3D/2$, the kinetic energy in the fluid approaching the body. A similar definition was given in \citet{Barrero-Gil2010a}). The current results show that the system has a peak efficiency of $0.26\%$  for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$. The peak efficiency reported in \citet{Barrero-Gil2010a} for $\reynoldsnumber=22300$ is approximately $5\%$ less than the current result. This difference is due to \cite{Barrero-Gil2010a} using a $3^{rd}$ order polynomial as the interpolating polynomial which under predicts the forcing at values of $\theta$ where the maximum force occurs as compared to the $7^{th}$ order polynomial used in this study.

@@

@@

The natural time scales of the system can be found by solving for the eigenvalues of the linearized equation of motion, namely
\begin{equation}
\label{eqn:eom_linear}
m\ddot{y}{+}c\dot{y}{+}ky{=}\frac{1}{2}\rho U^2 \mathcal{A} a_1\left(\frac{\dot{y}}{U}\right),
\end{equation}
which is simply the equation of motion presented in equation \ref{final_equation_motion} with the polynomial series for the lift force truncated at the linear term, and the forcing term representing vortex shedding removed.

@@

In this form, $\lambda$ represents the inverse time scale of the motion of the body due to the negative damping effect of the long-time aerodynamic forces. In fact, the terms can be regrouped and $\lambda$ written as
\begin{equation}
  \label{eqn:timescale}
  \lambda = \frac{a_1}{m^*}\frac{U}{D}
\end{equation}

Written this way, the important parameters that dictate this inverse time scale are clear. The rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $\partial C_y/\partial \alpha$, is represented by $a_1$. The mass ratio is represented by $m^*$. The inverse advective time scale of the incoming flow is represented by the ratio $U/D$. Increasing $a_1$ would mean the force on the body would increase more rapidly with small changes in the angle of attack, $\theta$, or transverse velocity. Equation \ref{eqn:timescale} shows that such a change will increase the inverse time scale, or analogously decrease the response time of the body. Increasing the mass of the body, thereby increasing $m^*$, has the opposite effect. The inverse time scale is decreased, or as might be expected, a heavier body will take longer to respond.

This timescale can then be used to non-dimensionalize the equation of motion, and to find the relevant dimensionless groups of the problem. If the non-dimensional time, $\tau$, is defined such that $\tau=t(a_1/m^*)(U/D)$, the equation of motion presented in equation \ref{final_equation_motion} can be non-dimensionalized as
\begin{equation}
  \label{eqn:eom_nondim}
  \ddot{Y} + \frac{m^{*2}}{a_1^2}\frac{kD^2}{mU^2}Y = \left(\frac{1}{2} - \frac{m^*}{a_1}\frac{cD}{mU}\right)\dot{Y} + H.O.T.,
\end{equation}

where $H.O.T.$ respresents the higher order terms in $\dot{Y}$. The coefficients can be regrouped into combinations of non-dimensional groups, and rewritten as
\begin{equation}
  \label{eqn:eom_nondim_regroup}
  \ddot{Y} + \frac{4\pi^{2}m^{*2}}{U^{*2}a_1^2}Y = \left(\frac{1}{2} - \frac{c^*m^*}{a_1}\right)\dot{Y} + H.O.T,
\end{equation}

where $c^*=cD/mU$ is a non-dimensional damping parameter.

Equation \ref{eqn:eom_nondim_regroup} shows there are four non-dimensional parameters that play a role in setting the response of the system. These are the stiffness (represented by the reduced velocity $U^*$), the damping $c^*$, the mass ratio $m^*$, and the geometry, represented by the rate of change in the aerodynamic force with respect to angle of attack when the body is at the equilibrium position, $a_1$. The grouping of these parameters into two groups in equation \ref{eqn:eom_nondim_regroup} which arise by non-dimensionalising using the natural time scale of the galloping system, suggests there are two groups that dictate the response: $\Gamma_1 = 4\pi^2m^{*2}/U^{*2}a_1^2$ and $\Gamma_2 = c^*m^*/a_1$. For a given geometry and Reynolds number, $\Gamma_1$ can be thought of as a combined mass-stiffness, whereas $\Gamma_2$ can be thought of a a combined mass-damping parameter. As it is assumed that during galloping the stiffnes plays only a minor role, $\Gamma_2$ seems a likely parameter to collapse the data presented in figure \ref{fig:uncollapsed_data}. In fact, in the classic paper on galloping from \citet{Parkinson1964}, galloping data from wind tunnel tests is presented in terms of a parameter that can be shown to be the same as $\Gamma_2$.

All of the quantities that make up $\Gamma_1$ and $\Gamma_2$ can, in theory, be known before an experiments is conducted. However, the quantity $a_1$ is a relatively difficult one to determine, requiring static body experiments or simulations. Here, the geometry is unchanged and results are only being compared at the same \reynoldsnumber. Hence, suitable parameters can be formed by multiplying $\Gamma_1$ and $\Gamma_2$ by $a_1^2$ and $a_1$ respectively, to arrive at a mass-stiffness parameter $\massstiff =  4\pi^2m^{*2}/U^{*2}$, and a mass-damping parameter defined as $\massdamp = c^*m^*$.

Figure \ref{fig:collapsed_data} presents the same data as shown in figure \ref{fig:uncollapsed_data}, but in terms of the parameter \massdamp. The collapse, especially of the velocity amplitude and power output data, is excellent. This result shows that it is possible to obtain a similar power output at different values of \ustar\ or $\zeta$ when the mass-damping constant, \massdamp, is kept fixed. An example of this is shown in figure \ref{fig:time_hostory_velocity_same_power}, where the time history of two cases with clearly different $U^*$ and $\zeta$ values, but the same value of $\massdamp=$\JL{KASUN: put the value of the mass-damping (your parameter $c/\rho\mathcal{A}U$) that you used here and in the figure caption}, are plotted. The figure clearly shows that the common power output is a result of similar velocity amplitudes between cases if one were to disregard the high frequencies due to shedding.

@@

Power can be expressed as the product of force and velocity. Therefore the instantaneous power from the fluid to the body can be expressed as $P_t=F_y\dot{y}$. Similarly the dissipated power due to the mechanical damping can be expressed as $P_d=(c\dot{y})\dot{y}$. The time average of these two quantities, described in equations \ref{power_alt} and \ref{power} should be equal due to energy conservation, provided that the mechanical friction losses are neglected. The mean power vs $U^*$ provides a detailed explanation for the variation of the output power when the reduced velocity is increased. The key regions consists of region 1 where the $P_{mean}$ increases with \ustar, region 2 where $P_{mean}$ becomes maximum and region 3 where $P_{mean}$ decreases with \ustar. Time histories of $P_t $ and $P_d$ at each of these key regions are presented in figure \ref{fig:power_time_histories}.

The non-dimensional damping, $c^*$, can be shown to be inversely proportional to $U^*$. Hence the damping parameter, and the mas-damping \massdamp, reduces when moving from region 1 to 3. Figure \ref{fig:lift_curves}(a) shows that $C_y$ and therefore instantaneous force rises until $4^\circ$ where it peaks and then falls, and at around $6^\circ$ becomes negative. The maximum amount of power that can be transferred occurs when $\dot{y}$ is such that $\theta$ is near the peak region. At the region where the instantaneous force becomes negative it will be opposing the velocity $\dot{y}$. Data at $\zeta=0.1$, $m^*=40$ and $\reynoldsnumber=165$ are shown in figure \ref{fig:power_time_histories} and are analysed as an example.

@@

\JL{KASUN: remember to also include the value of the mass-damping as well as $U^*$ in the following paragraphs. I have set things up so that \massdamp\ is the same as your original parameter}

@@

The mean power at different $m^*$ is presented as a function of the mass-damping parameter \massdamp\ in figure \ref{fig:m_star_collapsed}(a) for the low \reynoldsnumber\ case. For $m^*>30$, the power output is essentially independent of $m^*$, while at $m^* \leq 30$, the power output reduces with reducing $m^*$ across the parameter range. However, when the sinusoidal forcing function in equation \ref{equationofmotion}, which caters for the vortex shedding, is disregarded, the reduction in power is not observed as shown in figure \ref{fig:m_star_collapsed}(b). The suppression of galloping response at low $m^*$ and low \reynoldsnumber\ due to the presence of vortex shedding has previously been observed by \cite{Joly2012}. This is a non-linear interaction between the forcing that drives the galloping excitation and the forcing as a result of vortex shedding. The forcing associated with vortex  shedding is significantly larger and at a higher frequency than the forcing that drives galloping. Systems with low $m^*$ do not have enough inertia to fully sustain the galloping excitation over the longer period.

At $\reynoldsnumber=22300$ power output increases with decreasing $m^*$ for cases with $m^*<50$. The overall mean power tend to increase as the $m^*$ was decreased when $U^*$ was kept constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios. This is perhaps not surprising, as the definition of $\massstiff$ shows that this mass-stiffness parameter goes quickly to zero as $U^*$ grows, but that it will be of comparable order to the mass-damping \massdamp\ when $U^*$ approaches unity. Therefore, the influence of this second parameter \massstiff\ cannot be ignored for cases where $U^*$ is low.

The velocity time traces of example cases of both scenarios presented in figure \ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} show that essentially the same phenomenon occurs in both cases whereby the velocity signal tends to shift from a sinusoidal signal towards a square wave. The corresponding displacement signal tends to become more like a triangular wave. When the inertia of the system reduces, the body can accelerate faster thus attaining higher velocities more rapidly and spend a higher proportion of the period at a high velocity. Higher velocities are favourable because they result in higher hydrodynamic forcing and power output from mechanical damping. However, the velocity is limited by the characteristics of the hydrodynamic forcing which reaches a maximum and then decreases past an incident angle of of $13.21^{\circ}$ which corresponds to a transverse velocity of $\dot{y}/U=0.235$. It is estimated that the efficiency limit i.e ($\ustar \rightarrow \infty$, $m^* \rightarrow 0$ and $\massdamp=1.22$) will approach $13.5\%$ which corresponds to a square wave velocity signal with a velocity amplitude that results in maximum  hydrodynamic forcing.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. At higher $m^*$ ($m^*>30$ at lower \reynoldsnumber and $m^*> 50$ at high \reynoldsnumber) the power output of the system is not dependent on \ustar or natural frequency of the system, but controlled by the non-dimensionalised mass-damping constant \massdamp . By analysing key regions of the power vs \ustar curve is concluded that in order to obtain an optimum power output, the mass-damping constant $\Gamma_2$ should be high, but not so excessive that it hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was also observed. The peak efficiency was found to be $0.26\%$ for $\reynoldsnumber=165$ and $6.7\%$ for $\reynoldsnumber=22300$  when $\Gamma_2=0.314$ and $\Gamma_2=1.04$ respectively. In the low \reynoldsnumber\ case, the mean power tends to decrease at $m^*<30$ which appears to be due to the influence of vortex shedding. At $\reynoldsnumber=22300$ the opposite is observed where the mean power tends to increase with decreasing mass ratio, as well as the mean power increasing with increasing $U^*$ at low mass ratios. For this higher \reynoldsnumber\ case, When the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output. The limit to peak efficiency was found out to be $13.5\%$ and occurs when $m^*\rightarrow 0$ and $\ustar \rightarrow \infty$ and $\massdamp=1.22$ by analysing the data trend by lowering the $m^*$.
